THESIS PROJECT PROPOSAL

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

There is currently a great enigma in physics since we know that ordinary matter comprises only 5 \% of the universe, another 
25 \% includes what we call dark matter. Understanding the production of the Higgs boson, as well as its decays like the invisible 
decay modes are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new 
particles. Through this project we will investigate the production of the Higgs boson in association with a single top-type quartz (tH) 
in proton-proton collisions with the CMS experiment of the LHC. The distribution of events in one of the decay channels and the 
sensitivity that we get with the current data. The main objective is to search for new processes such as tH Higgs production mode in the 
CMS experiment which require to study different aspects such as the model of the noises that are made by simulation, techniques of 
adjustments to the data that incorporate the different noises and the signal, and estimates of statistical and systematic uncertainties.

@@

\appendix
\section{SKILLS THAT WILL BE DEVELOPED}

>>>>

There is currently a great enigma in physics since we know that ordinary matter comprises only 5 \% of the universe, another 
25 \% includes what we call dark matter. Understanding the production of the Higgs boson, as well as its decays like the invisible 
decay modes are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new 
particles. Through this project we will investigate the production of the Higgs boson in association with a single top quark (tH) 
in proton-proton collisions with the CMS experiment of the LHC. We will study the distribution of events in one of the decay channels and the sensitivity that we get with the current data. The main objective is to search for new processes such as tH Higgs production mode in the CMS experiment which require to study different aspects such as the model of the noises that are made by simulation, techniques of adjustments to the data that incorporate the different noises and the signal, and estimates of statistical and systematic uncertainties.

@@

\appendix
\section{SKILLS THAT WILL BE DEVELOPED}
The following are skills that will be developed based on the work on this project:
- understand particle physics from an experimental point of view.
- analyze and manipulate data using modern programming languages such as C++, Python and ROOT.
- data analysis techniques.
- use high performance computing.
